Revisiting the impact of deepfake technology towards viewer's political choice: A replication of Soubhik Barari (2021)

### 2021-03-19 outputs/paper/paper.Rmd
change plot size
update

## Intervention

@@

```{r postfavor, fig.cap="Distribution of feelings towards Sanders in six different situations",echo=FALSE, fig.width=6, fig.height=4}
#histogram for each treat
EDA<-EDA%>%
  drop_na(post_favor_Warren)

>>>>

@@

```{r postfavor, fig.cap="Distribution of feelings towards Warren in six different situations",echo=FALSE,fig.width=5, fig.height=4}

#histogram for each treat
EDA<-EDA%>%
  drop_na(post_favor_Warren)
